Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-08-02 02_paper/02_study/01_fitbit paper/analysis_270423.Rmd
fb

# Mean, SD and range for disruption and confidence factor
rating_table <- 
  df_rating %>% 
  filter(!is.na(confidence_factor),
         !is.na(disruption_factor)) %>% 
   summarise(N = n_distinct(ID), 
            "M disruption factor" = round(mean(disruption_factor),
                                     digits = 2),
            "SD disruption factor" = round(sd(disruption_factor),
                                      digits = 2),
            "Min disruption factor" = min(disruption_factor),
            "Max disruption factor" = max(disruption_factor),
            "M confidence factor" = round(mean(confidence_factor),
                                     digits = 2),
            "SD confidence factor" = round(sd(confidence_factor),
                                      digits = 2),
            "Min confidence factor" = min(confidence_factor),
            "Max confidence factor" = max(confidence_factor)
            )

@@

# t-Tests 
## using heart rate means
```{r}
df_ttest <- 
  df_regression %>% 
  group_by(ID, time_span) %>% 
  summarise(mean_heart_rate = mean(heart_rate_std)) %>% 
  ungroup()
```
## Teaching vs. Pre-Teaching (mean HR)

```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "preparation"],
         paired = T)

@@

## Teaching vs. Post-Teaching (mean HR)

```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "post"],
         paired = T)

@@

## Teaching vs. Interview (mean HR)

```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "interview"],
         paired = T)

@@

model2 <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
summary(model2)

>>>>

# Mean, SD and range for disruption and confidence factor
rating_table <- 
  df_rating %>% 
  filter(!is.na(confidence_factor),
         !is.na(disruption_factor),
         !ID %in% c("126",
                    "132",
                    "236")
         ) %>% 
   summarise(N = n_distinct(ID), 
            "M disruption factor" = round(mean(disruption_factor),
                                     digits = 2),
            "SD disruption factor" = round(sd(disruption_factor),
                                      digits = 2),
            "Min disruption factor" = min(disruption_factor),
            "Max disruption factor" = max(disruption_factor),
            "M confidence factor" = round(mean(confidence_factor),
                                     digits = 2),
            "SD confidence factor" = round(sd(confidence_factor),
                                      digits = 2),
            "Min confidence factor" = min(confidence_factor),
            "Max confidence factor" = max(confidence_factor)
            )

# Mean, SD and range for teaching experience
demo_table <-
  df_demo %>% 
  filter(!ID %in% c("126",
                    "132",
                    "236"
                    )
         ) %>% 
  summarise(N = n(),
            "M teaching experience" = round(mean(teaching_experience),
                                            digits = 2),
            "SD teaching experience" = round(sd(teaching_experience),
                                             digits = 2),
            "Min teaching experience" = min(teaching_experience),
            "Max teaching experience" = max(teaching_experience),
            )
```

@@

# t-Tests 
## using heart rate means
```{r}
df_ttest <- 
  df_regression %>% 
  group_by(ID, time_span) %>% 
  summarise(mean_heart_rate = mean(heart_rate_std)) %>% 
  ungroup()
```

## Teaching vs. Pre-Teaching (mean HR)
```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "preparation"],
         paired = T)

@@

## Teaching vs. Post-Teaching (mean HR)
```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "post"],
         paired = T)

@@

## Teaching vs. Interview (mean HR)
```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "interview"],
         paired = T)

@@

model2 <- aov(mean_hr_std ~ time_span, data = df_anova_subset)
(model2)

### 2024-08-02 02_paper/02_study/02_eye tracking video questionnaire paper/expertise_2024_07_19_MK.Rmd
fb

# create table with means
df_quest_table <-
  df_quest %>%
  group_by(Group) %>%
  transmute(
    Group = Group,
    # "N cm" = length(c_across(starts_with("LM")), na.rm = TRUE),
    "M cm" = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
    "SD cm" = round(sd(c_across(starts_with("LM")), na.rm = TRUE), 2),
    "Min cm" = round(min(c_across(starts_with("LM")), na.rm = TRUE), 2),
    "Max cm" = round(max(c_across(starts_with("LM")), na.rm = TRUE), 2),
    # "N cm" = length(c_across(starts_with("LP")), na.rm = TRUE),
    "M n&pv com" = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2),
    "SD n&pv com" = round(sd(c_across(starts_with("LP")), na.rm = TRUE), 2),
    "Min n&pv com" = round(min(c_across(starts_with("LP")), na.rm = TRUE), 2),
    "Max n&pv com" = round(max(c_across(starts_with("LP")), na.rm = TRUE), 2)
  )

>>>>

# create table with means
df_quest_table <-
  df_quest %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M cm" = round(mean(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    "SD cm" = round(sd(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    "Min cm" = round(min(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    "Max cm" = round(max(c_across(starts_with(
      "LM"
    )), na.rm = TRUE), 2),
    # "N cm" = length(c_across(starts_with("LP")), na.rm = TRUE),
    "M n&pv com" = round(mean(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2),
    "SD n&pv com" = round(sd(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2),
    "Min n&pv com" = round(min(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2),
    "Max n&pv com" = round(max(c_across(starts_with(
      "LP"
    )), na.rm = TRUE), 2)
  )
